Really Hard Instances for the Subgraph Isomorphism Problem

### 2015-11-14 paper/paper.tex
More stuff
Predictions and layout changes

\usepackage{ijcai13}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{gnuplot-lua-tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{placeins}
\usepackage{cleveref}

% \usepackage{showframe}

@@

\begin{abstract}
    Really hard SIP instances. Phase transitions. Alternative models and reduction.
\end{abstract}

@@

The \emph{non-induced subgraph isomorphism problem} is to find an injective mapping from a given
pattern graph to a given target graph which preserves adjacency---in essence, we are ``finding a
copy of'' the pattern inside the target. The \emph{induced} variant of the problem additionally
requires that the mapping preserve non-adjacency, so there are no ``extra edges'' in the copy of the
pattern that we find. Despite these problems being \NP-complete, modern practical subgraph
isomorphism algorithms can handle problem instances with many hundreds of vertices in the pattern
graph, and up to ten thousand vertices in the target graph
\cite{Cordella:2004,Solnon:2010,Audemard:2014,McCreesh:2015}.

However, these algorithms cannot handle \emph{arbitrary} instances of this size. The experimental
evaluations in these papers were performed using a mix of real-world instances (from applications
??), and randomly generated graph pairs. Using random instances can be beneficial, because it
provides a way of generating arbitrarily many instances cheaply, and reduces the risk of
over-fitting when tuning design parameters. The instances used were generated by taking a subgraph
of a random graph (using various models, including scale-free and bounded degree) and permuting the
vertices.  This is not ideal: such instances are guaranteed to be satisfiable, and so existing
benchmark suites contain relatively few non-trivial unsatisfiable instances. This introduces a new
source of bias when designing algorithms.

However, generating non-trivial unsatisfiable random instances is not straightforward. Using a
pattern graph from one of the random suites with the ``wrong'' target graph tends to give either a
trivially unsatisfiable instance, or a satisfiable instance. In particular, it is \emph{not} the
case that a relatively small random graph is very unlikely to appear in a larger random graph.

Here we present and evaluate a new method for creating random pattern/target pairs which can
generate both satisfiable and unsatisfiable instances. Our work builds upon the widely studied phase
transition phenomena observed in satisfiability and graph colouring problems ?? cite stuff. However,
we have three control parameters rather than one: we can independently alter the density of the
pattern graph, the density of the target graph, and the relative orders (number of vertices) of the
pattern and target graphs.  For non-induced isomorphisms, with the correct choice of parameters
there is a phase transition from satisfiable to unsatisfiable, and as expected we see a complexity
peak occur (with three different solvers) near this phase transition.

For certain choices of parameter for induced isomorphisms, there are two phase transitions, going
from satisfiable to unsatisfiable, and then from unsatisfiable back to satisfiable. Again, when
going from satisfiable to unsatisfiable (from either direction), instances go from being trivial to
really hard to solve. However, each of the three solvers we tested also finds the central
unsatisfiable region to be really hard---this is surprising, since this region is apparently
over-constrained. ?? Except really it's because solvers can't handle edges and non-edges
simultaneously. To show that this is not a simple weakness of subgraph isomorphism algorithms, we
verify that this region is also hard when using use a SAT solver, a pseudo-boolean solver, and a
clique encoding.

@@

?? Some stuff about order, density, random, $\rightarrowtail$ and $\hookrightarrow$.

@@

?? Software versions.

Our experiments were performed on systems with Intel Xeon E5-4650 v2 (Q1'14) CPUs and 768GBytes RAM
(although this much RAM was not needed), running Scientific Linux release 6.7. Software was compiled
using GCC 4.9.

@@

\begin{figure}[tb]
    \hskip-0.2cm\input{gen-graph-non-induced.tex}
    \setlength{\abovecaptionskip}{-2.5em}
    \caption{Behaviour of algorithms on the non-induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern density and the y-axis is the target
        density, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions. On the second row, we show the
        number of search nodes used by the Glasgow algorithm, on the third row, the number of
        search nodes used by the LAD algorithm, and the fourth, VF2; the dark regions indicate
        ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

@@

?? Can we predict where that line is?

@@

Pattern size 10, what we expect. Patterns 20 and 30 have large unsatisfiable regions in the middle,
but these remain hard. Paattern sizes 14, 15 and 16 show the transition between the two styles.

@@

\begin{figure*}[tb]
    \hskip-1.2cm\input{gen-graph-induced.tex}
    \setlength{\abovecaptionskip}{-2em}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}.}\label{figure:induced}
\end{figure*}

@@

@@

\begin{figure*}[tb]
    \hskip-1.2cm\input{gen-graph-sat.tex}
    \setlength{\abovecaptionskip}{-2em}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, the third row shows the number of decisions made by the Glucose SAT solver, and
    the fourth row shows the number of search nodes used by a clique encoding.}\label{figure:alt}
\end{figure*}

@@

Direct SAT encoding: variables for each assignment, cardinality constraints, edge and non-edge
constraints. We use the Glucose SAT solver. We see that hard instances remain hard, including inside
the central region, and that the easy satisfiable instances remain easy.

>>>>

\usepackage{ijcai13}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{gnuplot-lua-tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{placeins}
\usepackage{cleveref}
\usepackage{natbib}

% \usepackage{showframe}
\usepackage{lipsum}

\usetikzlibrary{decorations, decorations.pathreplacing, calc, backgrounds}

\definecolor{uofguniversityblue}{rgb}{0, 0.219608, 0.396078}

\definecolor{uofgheather}{rgb}{0.356863, 0.32549, 0.490196}
\definecolor{uofgaquamarine}{rgb}{0.603922, 0.72549, 0.678431}
\definecolor{uofgslate}{rgb}{0.309804, 0.34902, 0.380392}
\definecolor{uofgrose}{rgb}{0.823529, 0.470588, 0.709804}
\definecolor{uofgmocha}{rgb}{0.709804, 0.564706, 0.47451}
\definecolor{uofgsandstone}{rgb}{0.321569, 0.278431, 0.231373}
\definecolor{uofgforest}{rgb}{0, 0.2, 0.129412}
\definecolor{uofglawn}{rgb}{0.517647, 0.741176, 0}
\definecolor{uofgcobalt}{rgb}{0, 0.615686, 0.92549}
\definecolor{uofgturquoise}{rgb}{0, 0.709804, 0.819608}
\definecolor{uofgsunshine}{rgb}{1.0, 0.862745, 0.211765}
\definecolor{uofgpumpkin}{rgb}{1.0, 0.72549, 0.282353}
\definecolor{uofgthistle}{rgb}{0.584314, 0.070588, 0.447059}
\definecolor{uofgrust}{rgb}{0.603922, 0.227451, 0.023529}
\definecolor{uofgburgundy}{rgb}{0.490196, 0.133333, 0.223529}
\definecolor{uofgpillarbox}{rgb}{0.701961, 0.047059, 0}
\definecolor{uofglavendar}{rgb}{0.356863, 0.301961, 0.580392}

\renewcommand{\topfraction}{0.9}
\renewcommand{\bottomfraction}{0.8}

@@

\begin{abstract}
    We show how to generate ``really hard'' random instances for variants of the subgraph
    isomorphism problem. For the non-induced variant of the problem, we predict and observe a phase
    transition between satisfiable and unsatisfiable instances, with a corresponding complexity peak
    seen in three different solvers. For the induced variant of the problem, the behaviour is more
    complicated, with two phase transitions and an unexpectedly hard region in between. We show that
    this region remains hard when using pseudo-boolean and mixed integer encodings, and under
    reduction to the clique problem.
\end{abstract}

@@

The \emph{non-induced subgraph isomorphism problem} is to find an injective mapping from a given
pattern graph to a given target graph which preserves adjacency---in essence, we are ``finding a
copy of'' the pattern inside the target. The \emph{induced} variant of the problem additionally
requires that the mapping preserve non-adjacency, so there are no ``extra edges'' in the copy of the
pattern that we find. We illustrate both variants in \cref{figure:sip}.
Despite these problems being \NP-complete, modern practical subgraph isomorphism algorithms can
handle problem instances with many hundreds of vertices in the pattern graph, and up to ten thousand
vertices in the target graph \citep{Cordella:2004,Solnon:2010,Audemard:2014,McCreesh:2015}.

However, these algorithms cannot handle \emph{arbitrary} instances of this size. The experimental
evaluations of these algorithms were performed using a mix of real-world graphs, graphs that encode
biochemistry and computer vision problems, and randomly generated graph pairs. Using random
instances to evaluate algorithm behaviour can be beneficial, because it provides a way of generating
many instances cheaply, and reduces the risk of over-fitting when tuning design parameters. The
random instances used in each case came from common datasets (cite ??), which were generated by
taking a random subgraph of a random graph (using various models, including scale-free and bounded
degree) and permuting the vertices.  This is not ideal: such instances are guaranteed to be
satisfiable, and so existing benchmark suites contain relatively few non-trivial unsatisfiable
instances. These instances also tend to be computationally fairly easy, with most of the difficulty
being in dealing with the size of the model.

However, generating non-trivial unsatisfiable random instances is not straightforward. Using a
pattern graph from one of the random suites with the ``wrong'' target graph tends to give either a
trivially unsatisfiable instance, or a satisfiable instance. (In particular, it is \emph{not} the
case that a relatively small random graph is unlikely to appear in a larger random graph.)

\begin{figure}[b]
    \centering
    \begin{tikzpicture}[scale=0.5]
        \node [draw, circle, fill=uofgcobalt, inner sep=1.5pt] (Na) at (1,  0) {1};
        \node [draw, circle, fill=uofgpumpkin, inner sep=1.5pt] (Nb) at (1, -1.5) {2};
        \node [draw, circle, fill=uofglawn, inner sep=1.5pt] (Nc) at (0, -3) {3};
        \node [draw, circle, fill=uofgthistle, inner sep=1.5pt] (Nd) at (2, -3) {4};

        \draw [ultra thick] (Na) -- (Nb);
        \draw [ultra thick] (Nb) -- (Nc);
        \draw [ultra thick] (Nc) -- (Nd);
        \draw [ultra thick] (Nb) -- (Nd);

        \node [draw, circle, fill=uofgcobalt, inner sep=1.5pt] (N1) at (5.5,  0) {1};
        \node [draw, circle, fill=white, inner sep=1.5pt] (N2) at (7.5,  0) {2};
        \node [draw, circle, fill=uofgpumpkin, inner sep=1.5pt] (N3) at (5.5, -1.5) {3};
        \node [draw, circle, fill=white, inner sep=1.5pt] (N4) at (7.5, -1.5) {4};
        \node [draw, circle, fill=uofglawn, inner sep=1.5pt] (N5) at (5.5, -3) {5};
        \node [draw, circle, fill=uofgthistle, inner sep=1.5pt] (N6) at (7.5, -3) {6};

        \draw [thick, color=uofgsandstone!50] (N1) -- (N2);
        \draw [ultra thick] (N1) -- (N3);
        \draw [thick, color=uofgsandstone!50] (N1) -- (N4);
        \draw [thick, color=uofgsandstone!50] (N2) -- (N4);
        \draw [ultra thick] (N3) -- (N5);
        \draw [ultra thick] (N3) -- (N6);
        \draw [thick, color=uofgsandstone!50] (N4) -- (N6);
        \draw [ultra thick] (N5) -- (N6);
        \draw [thick, color=uofgsandstone!50] (N2) to [in=45, out=315] (N6);
        \draw [thick, color=uofgsandstone!50] (N1) to [in=135, out=225] (N5);

        \node [draw, circle, fill=white, inner sep=1.5pt] (M1) at (-5.5,  0) {1};
        \node [draw, circle, fill=uofgcobalt, inner sep=1.5pt] (M2) at (-3.5,  0) {2};
        \node [draw, circle, fill=uofgthistle, inner sep=1.5pt] (M3) at (-5.5, -1.5) {3};
        \node [draw, circle, fill=white, inner sep=1.5pt] (M4) at (-3.5, -1.5) {4};
        \node [draw, circle, fill=uofglawn, inner sep=1.5pt] (M5) at (-5.5, -3) {5};
        \node [draw, circle, fill=uofgpumpkin, inner sep=1.5pt] (M6) at (-3.5, -3) {6};

        \draw [thick, color=uofgsandstone!50] (M1) -- (M2);
        \draw [thick, color=uofgsandstone!50] (M1) -- (M3);
        \draw [thick, color=uofgsandstone!50] (M1) -- (M4);
        \draw [thick, color=uofgsandstone!50] (M2) -- (M4);
        \draw [ultra thick] (M3) -- (M5);
        \draw [ultra thick] (M3) -- (M6);
        \draw [thick, color=uofgsandstone!50] (M4) -- (M6);
        \draw [ultra thick] (M5) -- (M6);
        \draw [ultra thick] (M2) to [in=45, out=315] (M6);
        \draw [thick, color=uofgsandstone!50] (M1) to [in=135, out=225] (M5);

        \node [anchor=center, font=\Large] (A1) at (-1.5, -1.5) { $\hookleftarrow$ };
        \node [anchor=center, font=\Large] (A2) at ( 3.5, -1.5) { $\rightarrowtail$ };
    \end{tikzpicture}

    \caption{There is a non-induced isomorphism from the pattern graph, in the center, to the target
    on the right, mapping vertex 1 to 1, 2 to 3, 3 to 5 and 4 to 6. This is not an induced
    isomorphism, since there is an edge between 1 and 5 in the target but not between 1 and 3 in the
    pattern. The mapping from the pattern to the (same) target on the left, sending 1 to 2, 2 to 6, 3 to
    5 and 4 to 3, is both non-induced and induced.}
    \label{figure:sip}
\end{figure}

Here we present and evaluate a new method for creating random pattern/target pairs. This method
generates both satisfiable and unsatisfiable instances, and can produce computationally challenging
instances with only a few tens of vertices in the pattern, and 150 vertices in the target. Our work
builds upon the phase transition phenomena observed in satisfiability and graph colouring problems
first described by \citet{Cheeseman:1991} and \citet{Mitchell:1992}---?? cite later stuff and
explain really hard.

For subgraph isomorphism we have three relevant control parameters: we can independently alter the
edge probability of the pattern graph, the edge probability of the target graph, and the relative
orders (number of vertices) of the pattern and target graphs.  For non-induced isomorphisms, with
the correct choice of parameters we see results very similar to those observed with boolean
satisfiability problems: there is a phase transition from satisfiable to unsatisfiable (and we can
predict its location), and we see a complexity peak occur (with three different solvers) near this
phase transition.

For certain choices of parameters for induced isomorphisms, there are two phase transitions, going
from satisfiable to unsatisfiable, and then from unsatisfiable back to satisfiable. Again, when
going from satisfiable to unsatisfiable (from either direction), instances go from being trivial to
really hard to solve. However, each of the three solvers we tested also finds the central
unsatisfiable region to be really hard---this may be unexpected, since this region is not near a
phase transition and is apparently over-constrained. To show that this is not a simple weakness of
current subgraph isomorphism algorithms, we verify that this region is also hard when using use a
pseudo-boolean encoding, a mixed integer model, and under reduction to the clique problem.

@@

Throughout, our graphs are unlabelled, undirected, and do not have any loops (vertices which are
adjacent to themselves). We write $\operatorname{V}(G)$ for the vertex set of a graph $G$. A
\emph{non-induced subgraph isomorphism} from a graph $P$ (called the \emph{pattern}) to a graph $T$
(called the \emph{target}) is an injective mapping from $\operatorname{V}(P)$ to
$\operatorname{V}(T)$ which preserves adjacency---that is, for every adjacent $v$ and $w$ in
$\operatorname{V}(P)$, the vertices $i(v)$ and $i(w)$ are adjacent in $T$. An \emph{induced subgraph
isomorphism} additionally preserves non-adjacency---that is, if $v$ and $w$ are not adjacent in $P$,
then $i(v)$ and $i(w)$ must not be adjacent in $T$. We use the notation $i : P \rightarrowtail T$
for a non-induced isomorphism, and $i : P \hookrightarrow T$ for an induced isomorphism.

The \emph{order} of a graph is the cardinality of its vertex set.  We write $G(v, p)$ for a random
graph with $v$ vertices, and an edge between each distinct pair of vertices with independent
probability $p$.

@@

Our experiments were performed on systems with Intel Xeon E5-4650 v2 (Q1'14) CPUs and 768GBytes RAM
(although this much RAM was not needed), running Scientific Linux release 6.7.   ?? Software
versions. Clasp 3.1.3, Gurobi 6.0.5, Glasgow, LAD version 2, VFLib. Software was compiled using GCC
4.9.

?? Stuff about runtimes and recursive calls. We are not aiming to compare solvers; rather, we are
looking for solver-independent behaviour.

@@

\begin{figure}[t]
    \input{gen-graph-phase-transition.tex}
    \caption{With a fixed a pattern graph order of 20, a target graph order of 150, a target edge
        probability of 0.4, and varying pattern edge probability, we observe a phase transition and
        complexity peak with the Glasgow solver in the non-induced variant. Each point represents
        one instance. The lines show mean search effort, and mean proportion satisfiable, using a
    larger sample size.}
    \label{figure:phase-transition}
\end{figure}

Suppose we arbitrarily decide upon a pattern graph order of 20, a target graph order of 150, and a
fixed target edge probability of 0.40. As we vary the pattern edge probability from 0 to 1, we would
expect to see a shift from entirely satisfiable instances (with no edges in the pattern, we can
always find a match) to entirely unsatisfiable instances (a maximum clique in this order and edge
probability of target graph will usually have between 9 and 12 vertices). Indeed,
\cref{figure:phase-transition} shows that this is the case: the line (and the points show a subset
of the samples) ?? describe this a bit more, find the 0.5 SAT mark.

Some stuff about the complexity peak in the Glasgow solver. This looks remarkably similar to random
3SAT problems---compare, for example, Figure 1 of \citet{LeytonBrown:2014}. In particular,
satisfiable instances tend to be easier but show greater variation than unsatisfiable instances, and
there are exceptionally hard satisfiable instances. (The parallel version of the Glasgow solver is
designed to eliminate these.)

\begin{figure}[tb]
    \input{gen-graph-non-induced.tex}
    \caption{Behaviour of algorithms on the non-induced variant. Each point is the average of ten
        runs. For each plot, the x-axis is the pattern edge probability and the y-axis is the target
        edge probability, both from 0 to 1. Along the top row, we show the proportion of instances which are
        satisfiable; the white bands shows the phase transitions. The second row is our prediction
        of what the first row will look like. On the third row, we show the number of search nodes
        used by the Glasgow algorithm, on the fourth row, the number of search nodes used by the LAD
        algorithm, and the fifth, VF2; the dark regions indicate ``really hard'' instances.}
    \label{figure:non-induced}
\end{figure}

@@

In figure \cref{figure:phase-transition-bands} we show what happens for larger patterns.

\begin{figure}[tb]
    \input{gen-graph-phase-transition-bands.tex}
    \caption{The location of the phase transition, as the pattern grows. Shown are points where
    between 20\% and 80\% of instances are satisfiable.}
    \label{figure:phase-transition-bands}
\end{figure}

@@

To predict the location of the phase transition, we can calculate the expected number of solutions
by making a few dubious assumptions involving rounding and independence. Since we are trying to find
an \emph{injective} mapping from a pattern $P = G(p, d_p)$ to a target $T = G(t, d_t)$, there are
$t^{\underline{p}} = t \cdot (t - 1)\cdots(t - p + 1)$ possible assignments of target vertices to
pattern vertices.  We expect the pattern to have $d_p \cdot \binom{p}{2}$ edges, so we obtain the
probability of all of these edges being mapped to edges in the target by raising $d_t$ to this
power, giving an expected number of solutions of \[ t^{\underline{p}} \cdot {d_t}^{d_p \cdot
\binom{p}{2}} \textnormal{,} \] which we plot in ?? somewhere.

@@

Pattern order 10, what we expect. Patterns 20 and 30 have large unsatisfiable regions in the middle,
but these remain hard. Pattern orders 14, 15 and 16 show the transition between the two styles.

@@

\begin{figure*}[h]
    \input{gen-graph-induced.tex}
    \caption{Behaviour of algorithms on the induced variant, shown in the style
    of \cref{figure:non-induced}. The second row shows a bound on the satisfiable region, by
    considering where a \emph{non-}induced isomorphism may also be a non-induced isomorphism between
    complement graphs.}\label{figure:induced}
\end{figure*}

@@

By repeating the argument for locating the non-induced phase transition and additionally considering
non-edges, we get an expected number of solutions of \[t^{\underline{p}} \cdot {d_t}^{d_p \cdot
\binom{p}{2}} \cdot {d_{\overline{t}}}^{d_{\overline{p}} \cdot \binom{p}{2}} \textnormal{,} \]
where $d_{\overline{p}} = 1 - d_p$ and $d_{\overline{t}} = 1 - d_t$. We plot this ?? somewhere.

@@

\begin{figure*}[t]
    \input{gen-graph-sat.tex}
    \caption{Behaviour of other solvers on the induced variant on smaller graphs, shown in the style of
        \cref{figure:non-induced}. The second row shows the number of search nodes used by the Glasgow
        algorithm, the third row shows the number of decisions made by the Clasp pseudo-boolean solver,
        the fourth row shows the number of search nodes used by a clique encoding, and the fifth a mixed
        integer encoding with Gurobi.}\label{figure:alt}
\end{figure*}

@@

Direct pseudo-boolean encoding: variables for each assignment, cardinality constraints, edge and
non-edge constraints. We use the Clasp solver. We see that hard instances remain hard, including
inside the central region, and that the easy satisfiable instances remain easy. (Although not
presented here, we also tried an equivalent SAT encoding with the Glucose solver, and saw very
similar performance.)

\begin{figure}[tb]
    \centering
    \begin{tikzpicture}[scale=0.5]

        \foreach \n in {1, ..., 6}{
            \node [draw, circle, fill=uofgcobalt, inner sep=1.5pt] (N1\n) at (\n, 0) {\n};
        }

        \draw [decorate, decoration={brace, raise=0.2cm}, very thick] (N11.north west) -- (N16.north
            east) node [midway, above=0.3cm] { $1 \mapsto$ };

        \foreach \n in {1, ..., 6}{
            \node [draw, circle, fill=uofgpumpkin, inner sep=1.5pt] (N2\n) at (0, -\n) {\n};
        }

        \draw [decorate, decoration={brace, raise=0.2cm, mirror}, very thick] (N21.north west) --
            (N26.south west) node [midway, left=0.3cm] { $2 \mapsto$ };

        \foreach \n in {1, ..., 6}{
            \node [draw, circle, fill=uofglawn, inner sep=1.5pt] (N3\n) at (7, -\n) {\n};
        }

        \draw [decorate, decoration={brace, raise=0.2cm}, very thick] (N31.north east) -- (N36.south
            east) node [midway, right=0.3cm] { $3 \mapsto$ };

        \foreach \n in {1, ..., 6}{
            \node [draw, circle, fill=uofgthistle, inner sep=1.5pt] (N4\n) at (\n, -7) {\n};
        }

        \draw [decorate, decoration={brace, raise=0.2cm, mirror}, very thick] (N41.south west) --
            (N46.south east) node [midway, below=0.3cm] { $4 \mapsto$ };

        \begin{scope}[on background layer]
            \draw [color=uofgsandstone!50] ($(N11)!0.8!(N11.south)$) -- ($(N22)!0.8!(N22.east)$);
            \draw [color=uofgsandstone!50] ($(N11)!0.8!(N11.south)$) -- ($(N23)!0.8!(N23.east)$);
            \draw [color=uofgsandstone!50] ($(N11)!0.8!(N11.south)$) -- ($(N24)!0.8!(N24.east)$);
            \draw [color=uofgsandstone!50] ($(N11)!0.8!(N11.south)$) -- ($(N25)!0.8!(N25.east)$);
            \draw [color=uofgsandstone!50] ($(N11)!0.8!(N11.south)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N11)!0.8!(N11.south)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N12)!0.8!(N12.south)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N32)!0.8!(N32.west)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N42)!0.8!(N42.north)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N13)!0.8!(N13.south)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N33)!0.8!(N33.west)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N43)!0.8!(N43.north)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N14)!0.8!(N14.south)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N34)!0.8!(N34.west)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N44)!0.8!(N44.north)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N15)!0.8!(N15.south)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N35)!0.8!(N35.west)$);
            \draw [color=uofgsandstone!50] ($(N21)!0.8!(N21.east)$) -- ($(N45)!0.8!(N45.north)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N22)!0.8!(N22.east)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N42)!0.8!(N42.north)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N23)!0.8!(N23.east)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N43)!0.8!(N43.north)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N24)!0.8!(N24.east)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N44)!0.8!(N44.north)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N25)!0.8!(N25.east)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N45)!0.8!(N45.north)$);
            \draw [color=uofgsandstone!50] ($(N31)!0.8!(N31.west)$) -- ($(N16)!0.8!(N16.south)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N22)!0.8!(N22.east)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N32)!0.8!(N32.west)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N23)!0.8!(N23.east)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N33)!0.8!(N33.west)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N24)!0.8!(N24.east)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N34)!0.8!(N34.west)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N25)!0.8!(N25.east)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N35)!0.8!(N35.west)$);
            \draw [color=uofgsandstone!50] ($(N41)!0.8!(N41.north)$) -- ($(N16)!0.8!(N16.south)$);
            \draw [color=uofgsandstone!50] ($(N12)!0.8!(N12.south)$) -- ($(N33)!0.8!(N33.west)$);
            \draw [color=uofgsandstone!50] ($(N12)!0.8!(N12.south)$) -- ($(N24)!0.8!(N24.east)$);
            \draw [color=uofgsandstone!50] ($(N12)!0.8!(N12.south)$) -- ($(N45)!0.8!(N45.north)$);
            \draw [color=uofgsandstone!50] ($(N22)!0.8!(N22.east)$) -- ($(N14)!0.8!(N14.south)$);
            \draw [color=uofgsandstone!50] ($(N22)!0.8!(N22.east)$) -- ($(N34)!0.8!(N34.west)$);
            \draw [color=uofgsandstone!50] ($(N22)!0.8!(N22.east)$) -- ($(N44)!0.8!(N44.north)$);
            \draw [color=uofgsandstone!50] ($(N22)!0.8!(N22.east)$) -- ($(N16)!0.8!(N16.south)$);
            \draw [color=uofgsandstone!50] ($(N22)!0.8!(N22.east)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N22)!0.8!(N22.east)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N32)!0.8!(N32.west)$) -- ($(N13)!0.8!(N13.south)$);
            \draw [color=uofgsandstone!50] ($(N32)!0.8!(N32.west)$) -- ($(N24)!0.8!(N24.east)$);
            \draw [color=uofgsandstone!50] ($(N32)!0.8!(N32.west)$) -- ($(N44)!0.8!(N44.north)$);
            \draw [color=uofgsandstone!50] ($(N32)!0.8!(N32.west)$) -- ($(N15)!0.8!(N15.south)$);
            \draw [color=uofgsandstone!50] ($(N32)!0.8!(N32.west)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N32)!0.8!(N32.west)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N42)!0.8!(N42.north)$) -- ($(N13)!0.8!(N13.south)$);
            \draw [color=uofgsandstone!50] ($(N42)!0.8!(N42.north)$) -- ($(N24)!0.8!(N24.east)$);
            \draw [color=uofgsandstone!50] ($(N42)!0.8!(N42.north)$) -- ($(N34)!0.8!(N34.west)$);
            \draw [color=uofgsandstone!50] ($(N42)!0.8!(N42.north)$) -- ($(N15)!0.8!(N15.south)$);
            \draw [color=uofgsandstone!50] ($(N42)!0.8!(N42.north)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N42)!0.8!(N42.north)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N13)!0.8!(N13.south)$) -- ($(N34)!0.8!(N34.west)$);
            \draw [color=uofgsandstone!50] ($(N13)!0.8!(N13.south)$) -- ($(N44)!0.8!(N44.north)$);
            \draw [color=uofgsandstone!50] ($(N13)!0.8!(N13.south)$) -- ($(N25)!0.8!(N25.east)$);
            \draw [color=uofgsandstone!50] ($(N13)!0.8!(N13.south)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N23)!0.8!(N23.east)$) -- ($(N15)!0.8!(N15.south)$);
            \draw [color=uofgsandstone!50] ($(N23)!0.8!(N23.east)$) -- ($(N35)!0.8!(N35.west)$);
            \draw [color=uofgsandstone!50] ($(N23)!0.8!(N23.east)$) -- ($(N45)!0.8!(N45.north)$);
            \draw [color=uofgsandstone!50] ($(N23)!0.8!(N23.east)$) -- ($(N16)!0.8!(N16.south)$);
            \draw [color=uofgsandstone!50] ($(N23)!0.8!(N23.east)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N23)!0.8!(N23.east)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N33)!0.8!(N33.west)$) -- ($(N14)!0.8!(N14.south)$);
            \draw [color=uofgsandstone!50] ($(N33)!0.8!(N33.west)$) -- ($(N25)!0.8!(N25.east)$);
            \draw [color=uofgsandstone!50] ($(N33)!0.8!(N33.west)$) -- ($(N45)!0.8!(N45.north)$);
            \draw [color=uofgsandstone!50] ($(N33)!0.8!(N33.west)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N33)!0.8!(N33.west)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N43)!0.8!(N43.north)$) -- ($(N14)!0.8!(N14.south)$);
            \draw [color=uofgsandstone!50] ($(N43)!0.8!(N43.north)$) -- ($(N25)!0.8!(N25.east)$);
            \draw [color=uofgsandstone!50] ($(N43)!0.8!(N43.north)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N14)!0.8!(N14.south)$) -- ($(N35)!0.8!(N35.west)$);
            \draw [color=uofgsandstone!50] ($(N14)!0.8!(N14.south)$) -- ($(N45)!0.8!(N45.north)$);
            \draw [color=uofgsandstone!50] ($(N14)!0.8!(N14.south)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N24)!0.8!(N24.east)$) -- ($(N16)!0.8!(N16.south)$);
            \draw [color=uofgsandstone!50] ($(N24)!0.8!(N24.east)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N24)!0.8!(N24.east)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N34)!0.8!(N34.west)$) -- ($(N15)!0.8!(N15.south)$);
            \draw [color=uofgsandstone!50] ($(N34)!0.8!(N34.west)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N34)!0.8!(N34.west)$) -- ($(N46)!0.8!(N46.north)$);
            \draw [color=uofgsandstone!50] ($(N44)!0.8!(N44.north)$) -- ($(N15)!0.8!(N15.south)$);
            \draw [color=uofgsandstone!50] ($(N44)!0.8!(N44.north)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N44)!0.8!(N44.north)$) -- ($(N36)!0.8!(N36.west)$);
            \draw [color=uofgsandstone!50] ($(N15)!0.8!(N15.south)$) -- ($(N26)!0.8!(N26.east)$);
            \draw [color=uofgsandstone!50] ($(N25)!0.8!(N25.east)$) -- ($(N16)!0.8!(N16.south)$);
            \draw [color=uofgsandstone!50] ($(N25)!0.8!(N25.east)$) -- ($(N36)!0.8!(N36.west)$);
